Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-03 paper/paper.tex
tweaks & comments

As previously mentioned, the components of configurations are lifted as arguments to
@aeval@. Given the cache and simplified one-layer continuation (as we will see later), 
the shape of function @aeval@ now looks like:

@@

Upon entering @aeval@, we first determine whether the @out@ cache contains some values 
for the current configuration and use them immediately (if present).
This corresponds to small-step AAM with a work-list: when we have seen a state,
we can simply discard the state and continue working through the rest of the work-list @todo@.

@@

\begin{lstlisting}
  case Let(x, App(f, ae), e) =>
    val closures = atomicEval(f, env, store)
    nd[Storable](closures, Ans(Set[VS](), new_cache), { case (cls, clscache, clsnd) =>
        val Clos(Lam(v, body), c_env) = cls
        val vbaddr = allocBind(v, new_time);  val new_cenv = c_env + (v -> vbaddr)
        val new_store = store.update(vbaddr, atomicEval(ae, env, store))
        aeval(body, new_cenv, new_store, new_time, clscache, { case Ans(bdvss, bdcache) =>
          nd[VS](bdvss, Ans(Set[VS](), bdcache), { case (VS(vals, time, vssstore), bdvsscache, bdnd) =>
              val baddr = allocBind(x, time);  val new_env = env + (x -> baddr)
              val new_store = vssstore.update(baddr, vals)
              aeval(e, new_env, new_store, time, bdvsscache, {
                /* evaluate e with new env and store, then transfer to the next body's value */
                case Ans(evss, ecache) => bdnd(Ans(evss, ecache.outUpdate(config, evss)))
              })
          }, clsnd) /* transfer to the next target closure of f */
        })
    }, continue)
\end{lstlisting}

@@

% TODO: explain more on how caches work
Finally, the @analyze@ function (as the entrance of the analysis) does a looping iteration
to find the least fixed-point of cache starting from an empty cache.
If the @out@ cache of this iteration is equivalent to its @in@ cache, which means no more 
fact was discovered during this iteration, then we have reached a fixed-point of cache that 
has over-approximated the concrete evaluations, and thus the result can be returned.
Otherwise, we install the latest @out@ cache to the @in@ cache position when initializing 
the next iteration; in the meanwhile, an empty cache will be used as the @out@ cache. 
Note that the initial continuation of calling @aeval@ updates the values for the initial 
configuration in the final cache.

>>>>

As previously mentioned, the components of configurations are lifted as arguments to
@aeval@. Given the cache and the simplified one-layer continuation (as we will see later), 
the shape of function @aeval@ now looks like:

@@

%TODO: co-inductive
Upon entering @aeval@, we first determine whether the @out@ cache contains some values 
for the current configuration and use them immediately (if present).
This corresponds to small-step AAM with a work-list: when we have seen a state,
we can simply discard the state and continue working through the rest of the work-list @todo@.

@@

\begin{lstlisting}
  case Let(x, App(f, ae), e) =>
    val closures = atomicEval(f, env, store)
    nd[Storable](closures, Ans(Set[VS](), new_cache), { case (cls, clscache, clsnd) =>
        val Clos(Lam(v, body), c_env) = cls
        val vbaddr = allocBind(v, new_time);  val new_cenv = c_env + (v -> vbaddr)
        val new_store = store.update(vbaddr, atomicEval(ae, env, store))
        aeval(body, new_cenv, new_store, new_time, clscache, { case Ans(bdvss, bdcache) =>
          nd[VS](bdvss, Ans(Set[VS](), bdcache), { case (VS(vals, time, vssstore), bdvsscache, bdnd) =>
              val baddr = allocBind(x, time);  val new_env = env + (x -> baddr)
              val new_store = vssstore.update(baddr, vals)
              aeval(e, new_env, new_store, time, bdvsscache, { case Ans(evss, ecache) =>
                /* evaluate e with new env and store, then transfer to the next body's value */
                bdnd(Ans(evss, ecache.outUpdate(config, evss)))
              })
          }, clsnd) /* transfer to the next target closure of f */
        })
    }, continue)
\end{lstlisting}

@@

% TODO: explain more on how caches work
Finally, the @analyze@ function (as the entrance of the analysis) does a looping iteration
to find the least fixed-point of cache starting from an empty cache.
If the @out@ cache of this iteration is equivalent to its @in@ cache, which means no more 
fact was discovered during this iteration, then we have reached a fixed-point of cache that 
has over-approximated the concrete evaluations, and thus the result can be returned.
Otherwise, we install the latest @out@ cache to the @in@ cache position when initializing 
the next iteration; in the meanwhile, an empty cache will be used as the @out@ cache. 
Note that the initial continuation of calling @aeval@ updates the values for the initial 
configuration in the final cache.
% TODO: summarize this section
